Conference Paper Title\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-03-11 paper/paper.tex
halfway on 2x2 figures, started bib

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Previous Work}
There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
In these citation networks, in particular, node classification and link prediction have been heavily explored. 
In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
71 different papers done on node classification of the Cora dataset.  \par

Those that explored link prediction in the Cora and Citeseer datasets have achieved great results as well. 
In ‘NESS: Node Embeddings from Static SubGraphs,’ Ucar proposed splitting up the graph into multiple subgraphs 
that do not have overlapping edges in between subgraphs, using each graph to train and obtain node representations, 
then aggregating the results to obtain predictions [2]. Using this, he was able to obtain state-of-the-art accuracy results, 
achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. In ‘Neural Link Prediction with Walk Pooling,’ L. 
Pan et al proposed a GNN architecture that adds attention mechanisms to GNNs, achieving an accuracy of 89.59±1.58\% [3]. 
These past studies show the efficacy of GNNs on academic publications for node classification and link prediction, and, 
since these accuracies were certainly impressive, we hope to use these networks as a baseline to examine the key features 
of different datasets and extract information to create a similar dataset about the subject of machine learning hardware.  \par

@@

Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes [4]. As such, this 
dataset is similar to both Cora and CiteSeer, though it further explores the efficacy of GNNs on datasets outside of 
machine learning. This performance of this dataset can further validate parameters potentially affecting accuracies, 
such as edge count, classes, or path length,  in addition to explaining differences in different fields of publications. \par

Web of Science (WoS) is an online database of publication citations and information [5]. 
This online database created by Clarivate can be queried by genre and shows identifying information such as titles, 
references, and specific citations. As such, we can utilize the WoS dataset to address the goal of exploring additional 
datasets in machine learning hardware. Specifically, by downloading papers by (exclusive) topic, 
we can create a dataset representative of the field of machine learning and compare the performance of our dataset 
against GNNs alongside other common datasets to analyze its efficacy on these models and its viability as a dataset 
in an academic setting. Using this popular database, we query their dataset of publications for four categories: 
Machine Learning on the Edge, Neuromorphic Computing, Spiking Neural Networks, and Machine Learning Accelerator. 
In using the Web of Science database, we assume that the papers are representative of their assigned class and 
distinct from related classes. In this regard, the dataset that we curate is unique from other citation networks 
in that it will hold distinct characteristics and be of machine learning hardware, providing insight into the 
structure and nature of the machine learning hardware citation network. \par

Beginning with the provided models like Deep Graph Library, we take inspiration from existing methods, 
such as preprocessing methods discussed by the Semantic Scholar Academic Graph [6]. By constructing our 
datasets of publications, we will examine model characteristics of varying types of publication networks. 
We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph [7], 
a large academic graph dataset, shows a promising example of dataset scale, though it has differences in 
features, scaling, and overlapping that can interfere with providing information about any one academic field. 
Here, the data set uses a variety of data types for the nodes, like publications, authors, and venues, with 
the links between each denoting a correlation. \par

@@

\begin{table}[htbp]
    \caption{Citation Network Characteristics}
    \begin{center}
        \begin{tabular}{|c|cccccc|}
        \hline
        % \textbf{Table}&\multicolumn{6}{|c|}{\textbf{Table Column Head}} \\
        % \cline{1-4} 
        \textbf{} & \textbf{\textit{Nodes}} & \textbf{\textit{Edges}} & \textbf{\textit{Features}} &
        \textbf{\textit{Degree}} & \textbf{\textit{CC$^{\mathrm{a}}$}} & \textbf{\textit{MD$^{\mathrm{b}}$}} \\
        \hline
        \textbf{\textit{Cora}} & 
        2708& 5429& 1433& 3.89807& 0.24067& 19 \\
        \textbf{\textit{CiteSeer}} & 
        3312& 4660& 3704& 2.81400& 0.14255& 28 \\
        \textbf{\textit{Pubmed}} & 
        19717& 44348& 500& 4.49632& 0.06017& 18 \\
        \textbf{\textit{Small WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \textbf{\textit{Large WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \hline
        \end{tabular}
        \label{tab1}
        {$^{\mathrm{a}}$Clustering Coefficient.}
        {$^{\mathrm{b}}$Maximum Diameter.}
    \end{center}
\end{table}

@@

While both Cora and Citeseer categorize publications and have vocab dictionaries, 
there are no such categories or dictionaries for Web of Science results. 
Therefore, we utilized the search function to specify the categories to be 
both used and excluded in each search. To match the vocabularies of Cora and 
Citeseer, we utilized spacy for trained keyword extraction models, finding 
the top 10 unigrams with the most significance in each abstract, and used 
these words to construct our vocabulary vectors [11].

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
% mine own
\usepackage{caption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Previous Work}
There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
In these citation networks, in particular, node classification and link prediction have been heavily explored. 
In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
by utilizing a proposed method inspired by natural gradient descent. This paper achieved the highest accuracy across 
71 different papers done on node classification of the Cora dataset \cite{CoraAccuracy}.  \par

Those that explored link prediction in the Cora and Citeseer datasets have achieved great results as well. 
In ‘NESS: Node Embeddings from Static SubGraphs,’ Ucar proposed splitting up the graph into multiple subgraphs 
that do not have overlapping edges in between subgraphs, using each graph to train and obtain node representations, 
then aggregating the results to obtain predictions. Using this, he was able to obtain state-of-the-art accuracy results, 
achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. \cite{Ucar}
These past studies show the efficacy of GNNs on academic publications for node classification and link prediction, and, 
since these accuracies were certainly impressive, we hope to use these networks as a baseline to examine the key features 
of different datasets and extract information to create a similar dataset about the subject of machine learning hardware.  \par

@@

Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes \cite{Pubmed}. As such, this 
dataset is similar to both Cora and CiteSeer, though it further explores the efficacy of GNNs on datasets outside of 
machine learning. This performance of this dataset can further validate parameters potentially affecting accuracies, 
such as edge count, classes, or path length,  in addition to explaining differences in different fields of publications. \par

Web of Science (WoS) is an online database of publication citations and information \cite{WoS}. 
This online database created by Clarivate can be queried by genre and shows identifying information such as titles, 
references, and specific citations. As such, we can utilize the WoS dataset to address the goal of exploring additional 
datasets in machine learning hardware. Specifically, by downloading papers by (exclusive) topic, 
we can create a dataset representative of the field of machine learning and compare the performance of our dataset 
against GNNs alongside other common datasets to analyze its efficacy on these models and its viability as a dataset 
in an academic setting. Using this popular database, we query their dataset of publications for four categories: 
Machine Learning on the Edge, Neuromorphic Computing, Spiking Neural Networks, and Machine Learning Accelerator. 
In using the Web of Science database, we assume that the papers are representative of their assigned class and 
distinct from related classes. In this regard, the dataset that we curate is unique from other citation networks 
in that it will hold distinct characteristics and be of machine learning hardware, providing insight into the 
structure and nature of the machine learning hardware citation network. \par

Beginning with the provided models like Deep Graph Library, we take inspiration from existing methods, 
such as preprocessing methods discussed by the Semantic Scholar Academic Graph \cite{Wade}. By constructing our 
datasets of publications, we will examine model characteristics of varying types of publication networks. 
We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph \cite{Sinha}, 
a large academic graph dataset, shows a promising example of dataset scale, though it has differences in 
features, scaling, and overlapping that can interfere with providing information about any one academic field. 
Here, the data set uses a variety of data types for the nodes, like publications, authors, and venues, with 
the links between each denoting a correlation. \par

@@

\begin{table}[htbp]
    \caption{Citation Network Characteristics}
    \begin{center}
        \begin{tabular}{|c|cccccc|}
        \hline
        \textbf{} & \textbf{\textit{Nodes}} & \textbf{\textit{Edges}} & \textbf{\textit{Features}} &
        \textbf{\textit{Degree}} & \textbf{\textit{CC$^{\mathrm{a}}$}} & \textbf{\textit{MD$^{\mathrm{b}}$}} \\
        \hline
        \textbf{\textit{Cora}} & 
        2708& 5429& 1433& 3.89807& 0.24067& 19 \\
        \textbf{\textit{CiteSeer}} & 
        3312& 4660& 3704& 2.81400& 0.14255& 28 \\
        \textbf{\textit{Pubmed}} & 
        19717& 44348& 500& 4.49632& 0.06017& 18 \\
        \textbf{\textit{Small WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \textbf{\textit{Large WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \hline
        \end{tabular}
        \label{tab1}
        {$^{\mathrm{a}}$Clustering Coefficient.}
        {$^{\mathrm{b}}$Maximum Diameter.}
    \end{center}
\end{table}

@@

While both Cora and Citeseer categorize publications and have vocab dictionaries, 
there are no such categories or dictionaries for Web of Science results. 
Therefore, we utilized the search function to specify the categories to be 
both used and excluded in each search. To match the vocabularies of Cora and 
Citeseer, we utilized spacy for trained keyword extraction models, finding 
the top 10 unigrams with the most significance in each abstract, and used 
these words to construct our vocabulary vectors [11]. \par

\begin{figure}[htbp]
    % \centering
    \caption{Number of Papers per Year by Category}
    \captionsetup{labelformat=empty}
    \parbox[b]{.5\linewidth}{
    \includegraphics[scale=0.23]{papers_by_year.png}
    \caption{A cat}\label{cat}}
    \parbox[b]{.45\linewidth}{
    \includegraphics[scale=0.23]{times_cited.png}
    \caption{An elephant}\label{elephant}}
%   \caption{Number of Papers per Year by Category}\label{animals}
    \captionsetup{labelformat=simple}
\end{figure}

In Table 1, we examine the structure of each community by computing the mixed 
edge probability, i.e. how many out of the total edges in the graph contain 
an edge from one community to other communities. The mixed edge theoretical 
probability of a certain category, say A, is the probability that any node 
is in A out of all nodes, multiplied by the probability that any node is 
in any other category. We use this simple equation: \par

% TODO: fix new line problem!
\begin{equation}
    Theoretical\; Mixed\; Edge\; Probability(category\; A)
    \\
    = (P(node\; in\;A)) (1 - P(node\;in\;A))\label{eq}
\end{equation}

@@

\begin{thebibliography}{00}
\bibitem{CoraAccuracy} "Node Classification on Cora", url: https://paperswithcode.com/sota/node-classification-on-cora.
\bibitem{Ucar} T. Ucar, "NESS: Node Embeddings from Static SubGraphs", in arXiv, 2023, url: https://doi.org/10.48550/arXiv.2303.08958. 
\bibitem{Pubmed} National Library of Medicine, "Pubmed", url: https://relational.fit.cvut.cz/dataset/PubMed\_Diabetes.
\bibitem{WoS} Clarivate, "Web of Science", 2023, url: https://www.webofscience.com/wos/woscc/basic-search.
\bibitem{Wade} A. D. Wade, "The semantic scholar academic graph (s2ag)", in Companion Proceedings of the Web Conference 2022, 2022, pp. 739-739.
\bibitem{Sinha} A. Sinha et al., "An overview of microsoft academic service (mas) and applications", in Proceedings of the 24th international conference on world wide web, 2015, pp. 243-246.
\bibitem{Ambrogio} S. Ambrogio et al., "Equivalent-accuracy accelerated neural-network training using analogue memory", Nature, vol. 558, no. 7708, pp. 60-67, 2018.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
